% Created 2018-06-27 Wed 01:38
% Intended LaTeX compiler: pdflatex
\documentclass[presentation]{beamer}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\usepackage[utf8]{inputenc}
\usetheme{metropolis}
\author{Oleg Sivokon}
\date{\textit{<2018-06-27 Wed>}}
\title{Comparing Protobuf to AMF}
\hypersetup{
 pdfauthor={Oleg Sivokon},
 pdftitle={Comparing Protobuf to AMF},
 pdfkeywords={Protobuf Protocol Buffers ActionScript Message Format},
 pdfsubject={Comparing Protobuf to AMF},
 pdfcreator={Emacs 26.1 (Org mode 9.1.9)}, 
 pdflang={English}}
\begin{document}

\maketitle
\begin{frame}{Outline}
\tableofcontents
\end{frame}


\section{Some historical context}
\label{sec:org5cc1c25}

\begin{frame}[label={sec:org2b49d55}]{Battle for web dominance}
\begin{itemize}
\item HTML rules the web.  XSL and then SOAP are poorly accepted.
\item PHP, unlike ASP or JSP streams page content.
\item Macromedia, then Adobe Flash needs streaming for interactivity.
\item AMF gives Flash a competitive edge over SOAP.
\item AMFPHP first, then others implement AMF.
\item Adobe and Mozilla lose standards battle to Google, MS and Apple.
\item Protobuf is positioned to replace AMF.
\end{itemize}
\end{frame}

\section{Metadata vs no metadata}
\label{sec:org379fe19}

\begin{frame}[label={sec:orgeb8ea49}]{AMF: yest to metadata}
\begin{itemize}
\item Easy debugging.
\item No need for codegeneration.
\item Some overhead in short messages.
\item Potential for references, richer vocabulary.
\end{itemize}
\end{frame}

\begin{frame}[label={sec:orgeb2a4e4}]{Protobuf: no to metadata}
\begin{itemize}
\item Invention of Descriptor (fixed point description of description).
\item Extensive infrastrucutre.  Pros: more tools.  Cons: more work.
\begin{itemize}
\item Special RPC description language.
\item Special language-independent language for binary data
description.
\end{itemize}
\item Multiple encoding layers: wire-type, value-type,
application-type.
\end{itemize}
\end{frame}

\section{Reference}
\label{sec:orgd53f325}

\begin{frame}[label={sec:orgae4c088}]{Links}
\begin{itemize}
\item \href{http://ncannasse.fr/blog/ecmascript\_4\_and\_the\_web?lang=en}{Cannasse: Ecmascript 4 and the web}
\item \href{http://ncannasse.fr/blog/ecmascript\_disharmony?lang=en}{Cannasse: Ecmascript discharmony}
\item \href{https://www.silexlabs.org/amfphp/}{AMFPHP}
\item \href{https://en.wikipedia.org/wiki/Action\_Message\_Format}{Wikipedia: AMF}
\end{itemize}
\end{frame}
\end{document}
